\TheTitle

### 2016-04-22 linvis.tex
Editing Conclusion

Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits when compared to DAG-based models. Not only are
we provide a clearer visualization, we provide information about the files
edited by all of the commits contained within a merge, and we provide the
information about what modules are edited in a merge.

While we are able to generate a better explanation of the changes happening at
each commit and merge, the tree-model requires more information than what is
provided by git, requiring a central server to monitor changes to the project.
This breaks the design goals of decentralized version control systems and makes
the tool specific to the project.

A tree-based model appears to be sufficient for creating a clean visualization
and explanation of the changes in the Linux kernel.

>>>>

Our tool shows promising results in working toward our goals, building a tool that
can more easily navigate the repository, and provide clearer explanations of the
changes made. The filtering by searches and the various tree visualizations enable
users to easily navigate through the kernel, finding the commits and merges that
pertain to what they are interested in. The tree visualizations are able to both
serve as a navigation piece, providing simpler navigation through the kernel, but
also demonstrate which commits contribute to which merges, providing further
explanation over the DAG. The tree model further improves the explanation by enabling
the tool to aggregate metadata at the merges instead of requiring a user to manually
aggregate the information. Our tool currently aggregates file information and the
modules edited, but can be extended to include authorship information and aggregated
patch information.

The tree model requires more information than what is provided by git, requiring a
central server to monitor changes to the project. This breaks the design goals of
decentralized version control systems and makes the visualization tool specific to
the project.

While these are significant drawbacks for small projects, large projects will likely
have a more centralized work flow with a master repository where contributions will
eventually land, along with various servers that can watch this master repository
for changes. Given that the importance of clear visualizations of the repository
outweighs the cost of having a server monitor the state of the repository, the
tree-based model appears to provide clean visualizations and explanations of the
changes in the Linux kernel.
